
\documentclass[11pt]{article}
\usepackage[roman,nocolor]{sean}
\usepackage{von}
\titledef{Sample Exam\\
        \large Made with TiKT\footnote{By Sean Li. Selected problems belong to their respective authors and oragnizations, as attributed.}}
\authordef{Sean Li}
\datedef{Generated \today}
\lheaddef{Sample Exam}
\rheaddef{Sean Li}
\linespread{1}

\begin{document}
\maketitle

\section{Problems}

\begin{enumerate}
 \item For each positive integer $k$, let $S_k$ denote the increasing arithmetic sequence of integers whose first term is $1$ and whose common difference is $k$. For example, $S_3$ is the sequence $1,4,7,10,\ldots.$ For how many values of $k$ does $S_k$ contain the term $2005$?

 \item In $\triangle ABC$, $AB = 2019$, $BC = 2020$, and $CA = 2021$. Yannick draws three regular $n$-gons in the plane of $\triangle ABC$ so that each $n$-gon shares a side with a distinct side of $\triangle ABC$ and no two of the n-gons overlap. What is the maximum possible value of $n$?

 \item Maya lists all the positive divisors of $2010^2$. She then randomly selects two distinct divisors from this list. Let $p$ be the probability that exactly one of the selected divisors is a perfect square. The probability $p$ can be expressed in the form $\frac {m}{n}$, where $m$ and $n$ are relatively prime positive integers. Find $m + n$.

 \item On a $5 \times 5$ grid we randomly place two \emph{cars}, which each occupy a single cell and randomly face in one of the four cardinal directions. It is given that the two cars do not start in the same cell. In a \emph{move}, one chooses a car and shifts it one cell forward. The probability that there exists a sequence of moves such that, afterward, both cars occupy the same cell is $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Compute $100m + n$.

 \item In triangle $ABC,$ $AB = 13,$ $BC = 14,$ $AC = 15,$ and point $G$ is the intersection of the medians. Points $A',$ $B',$ and $C',$ are the images of $A,$ $B,$ and $C,$ respectively, after a $180^\circ$ rotation about $G.$ What is the area of the union of the two regions enclosed by the triangles $ABC$ and $A'B'C'?$

 \item Let $z$ be a complex number with $|z|=2014$. Let $P$ be the polygon in the complex plane whose vertices are $z$ and every $w$ such that $\frac{1}{z+w}=\frac{1}{z}+\frac{1}{w}$. Then the area enclosed by $P$ can be written in the form $n\sqrt{3}$, where $n$ is an integer. Find the remainder when $n$ is divided by $1000$.

 \item There are eight people, each with their own horse. The horses are arbitrarily arranged in a line from left to right, while the people are lined up in random order to the left of all the horses. One at a time, each person moves rightwards in an attempt to reach their horse. If they encounter a mounted horse on their way to their horse, the mounted horse shouts angrily at the person, who then scurries home immediately. Otherwise, they get to their horse safely and mount it. The expected number of people who have scurried home after all eight people have attempted to reach their horse can be expressed as simplified fraction $\tfrac{m}{n}$. Find $m+n$.

 \item Let $a$, $b$, and $c$ be complex numbers satisfying the system of equations\begin{align*}\dfrac{a}{b+c}+\dfrac{b}{c+a}+\dfrac{c}{a+b}&=9,\\\dfrac{a^2}{b+c}+\dfrac{b^2}{c+a}+\dfrac{c^2}{a+b}&=32,\\\dfrac{a^3}{b+c}+\dfrac{b^3}{c+a}+\dfrac{c^3}{a+b}&=122.\end{align*}Find $abc$.

 \item Acute, isosceles triangle $ABC$ with $AB = AC$ is inscibed is a unit circle $\Omega$ with center $O$. Point $D$ is the reflection of $C$ across $AB$. Given that $DO = \sqrt{3}$, find the area of triangle $ABC$.

 \item Let $a, b$ and $c$ be the distinct solutions to the equation $x^3-2x^2+3x-4=0$. Find the value of
$$\frac{1}{a(b^2+c^2-a^2)}+\frac{1}{b(c^2+a^2-b^2)}+\frac{1}{c(a^2+b^2-c^2)}.$$
\end{enumerate}

\vfill

\begin{flushright}
  \emph{Time limit: 50 minutes.} \\
  \emph{Each problem is worth one point.}
\end{flushright}

\newpage

\section{Answers}

\begin{enumerate}
 \item $12$
 \item $11$
 \item $107$
 \item $1148$
 \item $112$
 \item $147$
 \item $1759$
 \item $13$
 \item $\frac{\sqrt{2} + 1}{2}$
 \item $1/8$\end{enumerate}

\newpage

\section{Problem Info}

\begin{enumerate}
 \item \textbf{Source}: AIME 2005 I 2
 
 \textbf{Tags}: [2020-06, 5C, number-theory, algebra, factors]
 
 \textbf{Solution}: \url{https://artofproblemsolving.com/wiki/index.php/2005\_AIME\_I\_Problems/Problem\_2}
 \item \textbf{Source}: HMNT 2019 General 4
 
 \textbf{Tags}: [2020-06, 10C, geometry, angles]
 
 \textbf{Solution}: \url{https://hmmt-archive.s3.amazonaws.com/tournaments/2019/nov/gen/solutions.pdf}
 \item \textbf{Source}: AIME 2010 I 1
 
 \textbf{Tags}: [2020-06, 10C, number-theory, combo]
 
 \textbf{Solution}: \url{https://artofproblemsolving.com/wiki/index.php/2010\_AIME\_I\_Problems/Problem\_1}
 \item \textbf{Source}: OMO 2020 Spring 7
 
 \textbf{Tags}: [2020-06, 15C, combo, careful, cases, important]
 
 \textbf{Solution}: \url{https://artofproblemsolving.com/community/c1124220\_2020\_online\_math\_open\_problems}
 \item \textbf{Source}: AIME 2003 II 6
 
 \textbf{Tags}: [2020-06, 20C, geometry, area]
 
 \textbf{Solution}: \url{https://artofproblemsolving.com/wiki/index.php/2003\_AIME\_II\_Problems/Problem\_6}
 \item \textbf{Source}: AIME 2014 II 10
 
 \textbf{Tags}: [2020-06, 30C, algebra, complex, world]
 
 \textbf{Solution}: \url{https://artofproblemsolving.com/wiki/index.php/2014\_AIME\_II\_Problems/Problem\_10}
 \item \textbf{Source}: CMIMC 2016 Combinatorics 7
 
 \textbf{Tags}: [2020-06, 35C, combo, expect, infcombo]
 
 \textbf{Solution}: \url{http://cmimc-official.herokuapp.com/docs/past-tests/2016\_Combinatorics\_S.pdf}
 \item \textbf{Source}: CMIMC 2017 Algebra 7
 
 \textbf{Tags}: [2020-06, 35C, algebra, manipulate]
 
 \textbf{Solution}: \url{http://cmimc-official.herokuapp.com/docs/past-tests/2017\_Algebra\_S.pdf}
 \item \textbf{Source}: HMMT 2019 Geometry 5
 
 \textbf{Tags}: [2020-06, 35C, geometry, area]
 
 \textbf{Solution}: \url{https://hmmt-archive.s3.amazonaws.com/tournaments/2019/feb/geo/solutions.pdf}
 \item \textbf{Source}: CMIMC 2019 Algebra/NT 6
 
 \textbf{Tags}: [2020-06, 40C, algebra, polynomial, important, courage]
 
 \textbf{Solution}: \url{http://cmimc-official.herokuapp.com/docs/past-tests/2019\_ANT\_S.pdf}\end{enumerate}

\end{document}
